An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex
Updating figures for section 5

\begin{figure}
	\begin{center}
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-star.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-diamond.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{tikz/lovasz-link-envelope.pdf}
		\end{minipage}\hfill
		\caption{Links $\psi^*$ (L) and $\psi^\diamond$ (M) such that $(L^f, \psi^*)$ and $\psi^\diamond$ are calibrated with respect to $\ellabs$ for all suitable $f$. Points in each region link to the embedding point contained in the region. Both are constructed via the link envelope $\Psi$ (R) from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.\jessie{New, simpler, caption.  Clear enough?}\raf{Looks great.  Maybe instead of (L),(M), etc, which look a bit like function applications, we could put the actual symbols in the top left of the figures.  Also, could we shrink the $u_1,u_2$ and bullets, and make the other labels larger, basically to match Figure~\ref{fig:abstain-links}?}
			}
			%Points in the dark green regions link to $\vec 0$; points in light green link to a permutation of $(0,\pm 1)$, and points in yellow regions link to $(\pm 1, \pm 1)$.\jessie{Not sure how to phrase this?  Would we just be better off explicitly labeling things?}\raf{Agreed that it's a little unclear, but not sure labeling would be better... let's discuss next call}}
		\label{fig:lovasz-links}
	\end{center}
\end{figure}

@@

\raf{See if we can simplify / combine these paragraphs given the new 5.1}
%% one might make distributional assumptions to regain consistency with geometric drawing
Upon showing that $L^{WW}$ embeds $\ell^\OP$, \citeauthor{wang2020weston} to characterize $\prop{\ell^\OP}$ and use it to give sufficient distributions assumptions over labels in $\P \subseteq \simplex$ such that $L^{WW}$ and the canonical argmax link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
%Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
Like Figure~\ref{fig:abstain-intuition-inconsistent}, Figure~\ref{fig:ordered-partition} gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$ juxtaposed with the level sets of the mode.
%$\mode_r = \{p \in \simplex \mid r \in \mode(p)\}$ for each $r \in \Y$.
%Since each distribution in a cell of $\prop{\ell^\OP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
%Thus, if a cell of $\prop{\ell^\OP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ell^\OP}$ value can be mapped to the corresponding $\mode$ value.
%Conversely, if the relative interior of a cell of $\prop{\ell^\OP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes the cells colored in blue in Figure~\ref{fig:ordered-partition}.

@@

\begin{table*}
	\centering
	\begin{tabular}{ccccc}
		& $\prop{\Li{2}}$ & $\prop{\Li{3}}$ & $\prop{\Li{4}}$ & $\prop{L^k}$\\
		\hline \hline
		\rotatebox[origin=c]{90}{$k = 2$\hspace*{-2.5cm}} & \input{tikz/n4-k2-psi2-slice} & \input{tikz/n4-k2-psi3-slice} & \input{tikz/n4-k2-psi4-slice} & \input{tikz/n4-k2-psi6-slice}\\ 
		\rotatebox[origin=c]{90}{$k = 3$\hspace*{-2.5cm}} & \input{tikz/n4-k3-psi2-slice} & \input{tikz/n4-k3-psi3-slice} & \input{tikz/n4-k3-psi4-slice} & \input{tikz/n4-k3-psi6-slice}\\ 
	\end{tabular}
	\caption{
		Visualizations of the properties elicited by the losses (embedded by) $\Li{2}$, $\Li{3}$, $\Li{4}$ studied by \citeauthor{yang2018consistency}, and $L^k$ in eq.~\eqref{eq:topk-embedding} with $n=4$ and $k \in \{2,3\}$, fixing $p_4 = 1/4$. 
		The dashed blue lines form cells whose elements are distributions $p$ corresponding to the same $u \in \prop{\elli k}(p)$ labeling the cell. 
		As the link $\psi$ must be deterministic, in order for $(\Li{k}, \psi)$ to be consistent with respect to $\elli k$, each cell outlined in black is fully contained in exactly one cell from the dashed blue lines. 
		Regions outlined in black that are filled in blue and cross the dashed blue lines suggest where deciding how to construct a link $\psi$ is ambiguous, as the top-$k$ elements of the optimal report $u$ are ambiguous.  \jessie{Thoughts on this caption?  Now walking through this geometric intuition for the third time.} \raf{Let's refer back to Figure~\ref{fig:abstain-intuition-inconsistent} instead of going into the same level of detail; see the changes I made in Figure~\ref{fig:ordered-partition}.}
	}
	\label{tab:loss-slices}
\end{table*}

>>>>

\begin{figure}
	\begin{center}
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-star.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-diamond.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{tikz/lovasz-link-envelope.pdf}
		\end{minipage}\hfill
		\caption{Links $\psi^*$ and $\psi^\diamond$ such that $(L^f, \psi^*)$ and $\psi^\diamond$ are calibrated with respect to $\ellabs$ for all suitable $f$. Points in each region link to the embedding point contained in the region. Both are constructed via the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.\jessie{New, simpler, caption.  Clear enough?}\raf{Looks great.  Maybe instead of (L),(M), etc, which look a bit like function applications, we could put the actual symbols in the top left of the figures.  Also, could we shrink the $u_1,u_2$ and bullets, and make the other labels larger, basically to match Figure~\ref{fig:abstain-links}?\jessie{Done}}
			}
			%Points in the dark green regions link to $\vec 0$; points in light green link to a permutation of $(0,\pm 1)$, and points in yellow regions link to $(\pm 1, \pm 1)$.\jessie{Not sure how to phrase this?  Would we just be better off explicitly labeling things?}\raf{Agreed that it's a little unclear, but not sure labeling would be better... let's discuss next call}}
		\label{fig:lovasz-links}
	\end{center}
\end{figure}

@@

\raf{See if we can simplify / combine these paragraphs given the new 5.1}\jessie{Attempted}
%% one might make distributional assumptions to regain consistency with geometric drawing
Upon showing that $L^{WW}$ embeds $\ell^\OP$, \citeauthor{wang2020weston} to characterize $\prop{\ell^\OP}$ and use it to give sufficient distributions assumptions over labels in $\P \subseteq \simplex$ such that $L^{WW}$ and the canonical argmax link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
%Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
Like Figure~\ref{fig:abstain-intuition-inconsistent}, Figure~\ref{fig:ordered-partition} gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$\jessie{notation} juxtaposed with the level sets of the mode.
%$\mode_r = \{p \in \simplex \mid r \in \mode(p)\}$ for each $r \in \Y$.
%Since each distribution in a cell of $\prop{\ell^\OP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
%Thus, if a cell of $\prop{\ell^\OP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ell^\OP}$ value can be mapped to the corresponding $\mode$ value.
%Conversely, if the relative interior of a cell of $\prop{\ell^\OP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes the cells colored in blue in Figure~\ref{fig:ordered-partition}.

@@

\begin{table*}
	\centering
	\begin{tabular}{ccccc}
		& $\prop{\Li{2}}$ & $\prop{\Li{3}}$ & $\prop{\Li{4}}$ & $\prop{L^k}$\\
		\hline \hline
		\rotatebox[origin=c]{90}{$k = 2$\hspace*{-2.5cm}} & \input{tikz/n4-k2-psi2-slice} & \input{tikz/n4-k2-psi3-slice} & \input{tikz/n4-k2-psi4-slice} & \input{tikz/n4-k2-psi6-slice}\\ 
		\rotatebox[origin=c]{90}{$k = 3$\hspace*{-2.5cm}} & \input{tikz/n4-k3-psi2-slice} & \input{tikz/n4-k3-psi3-slice} & \input{tikz/n4-k3-psi4-slice} & \input{tikz/n4-k3-psi6-slice}\\ 
	\end{tabular}
	\caption{
		Visualizations of the properties elicited by the losses (embedded by) $\Li{2}$, $\Li{3}$, $\Li{4}$ studied by \citeauthor{yang2018consistency}, and $L^k$ in eq.~\eqref{eq:topk-embedding} with $n=4$ and $k \in \{2,3\}$, fixing $p_4 = 1/4$. 
		%The dashed blue lines form cells whose elements are distributions $p$ corresponding to the same $u \in \prop{\elli k}(p)$ labeling the cell. 
		%As the link $\psi$ must be deterministic, in order for the $(\Li{k}, \psi)$ to be consistent with respect to $\elli k$, each cell outlined in black is fully contained in exactly one cell from the dashed blue lines. 
		Regions outlined in black that are filled in blue and cross the dashed blue lines suggest where deciding how to construct a link $\psi$ is ambiguous, as the top-$k$ elements of the optimal report $u$ are ambiguous.  
		See the caption for Figure~\ref{fig:ordered-partition} on how to interpret what the colored regions say about inconsistency with respect to top-$k$ classification.
		\jessie{Thoughts on this caption?  Now walking through this geometric intuition for the third time.} \raf{Let's refer back to Figure~\ref{fig:abstain-intuition-inconsistent} instead of going into the same level of detail; see the changes I made in Figure~\ref{fig:ordered-partition}.}
	}
	\label{tab:loss-slices}
\end{table*}

### 2022-05-24 poly-embed-journal/tikz/lovasz-links.tex
Updating figures for section 5

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \psi^*
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\draw[dashed, opacity=0.2] (-1.2,0) -- (1.2,0) node[anchor= west, opacity=1]{\scriptsize $u_1$};
\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[anchor=south, opacity=1]{\scriptsize $u_2$};

@@

\node at (1,1){\textbullet} (1,1)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
\node at (1,0){\textbullet} (1,0)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
\node at (0,1){\textbullet} (-0.03,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,1)$};

\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
\node at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
\node at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};

\node at (0,-1){\textbullet} (-0.1,-1)node[anchor=north west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
\node at (1,-1){\textbullet} (1,-1)node[anchor=north,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};

\node at (0,0){\textbullet} (0,0)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,0)$};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \psi^$\diamond$
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\draw[dashed,opacity=0.2] (-1.2,0) -- (1.2,0) node[anchor=west, opacity=1]{\scriptsize $u_1$};
\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[anchor=south, opacity=1]{\scriptsize $u_2$};

@@

\node at (1,1){\textbullet} (1,1)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
\node at (1,0){\textbullet} (1,0)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
\node at (0,1){\textbullet} (-0.03,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,1)$};

\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
\node at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
\node at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};

\node at (0,-1){\textbullet} (-0.025,-1)node[anchor=north west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
\node at (1,-1){\textbullet} (1,-1)node[anchor=north,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};

\node at (0,0){\textbullet} (0,0)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,0)$};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \hat \Psi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \psi^$\diamond$
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\draw[dashed,opacity=0.2] (-1.2,0) -- (1.2,0) node[anchor=west, opacity=1]{\scriptsize $u_1$};
\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[anchor=south, opacity=1]{\scriptsize $u_2$};

@@

%% embedding points
\node at (1,1){\textbullet};
\node at (1,0){\textbullet};
\node at (0,1){\textbullet};
\node at (-1,-1){\textbullet};
\node at (-1,0){\textbullet};
\node at (-1,1){\textbullet};
\node at (0,-1){\textbullet};
\node at (1,-1){\textbullet};
\node at (0,0){\textbullet};

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \psi^*
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\node at (-1, 1.35)[opacity=1, scale=0.8]{\scriptsize $\psi^*$};
\draw[dashed, opacity=0.2] (-1.2,0) -- (1.2,0) node[scale=0.4, anchor= west, opacity=1]{\scriptsize $u_1$};
\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[scale=0.4,anchor=south, opacity=1]{\scriptsize $u_2$};

@@

\node[scale=0.6] at (1,1){\textbullet} (1,1)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
\node[scale=0.6] at (1,0){\textbullet} (1,0)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
\node[scale=0.6] at (0,1){\textbullet} (-0.03,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,1)$};

\node[scale=0.6] at (-1,-1){\textbullet} (-1,-1)node[anchor=north, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
\node[scale=0.6] at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
\node[scale=0.6] at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};

\node[scale=0.6] at (0,-1){\textbullet} (-0.1,-1)node[anchor=north west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
\node[scale=0.6] at (1,-1){\textbullet} (1,-1)node[anchor=north,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};

\node[scale=0.6] at (0,0){\textbullet} (0,0)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,0)$};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \psi^$\diamond$
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\node at (-1, 1.35)[opacity=1, scale=0.8]{\scriptsize $\psi^\diamond$};
\draw[dashed,opacity=0.2] (-1.2,0) -- (1.2,0) node[scale=0.4,anchor=west, opacity=1]{\scriptsize $u_1$};
\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[scale=0.4,anchor=south, opacity=1]{\scriptsize $u_2$};

@@

\node[scale=0.6] at (1,1){\textbullet} (1,1)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
\node[scale=0.6] at (1,0){\textbullet} (1,0)node[anchor= south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
\node[scale=0.6] at (0,1){\textbullet} (-0.03,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,1)$};

\node[scale=0.6] at (-1,-1){\textbullet} (-1,-1)node[anchor=north, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
\node[scale=0.6] at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
\node[scale=0.6] at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};

\node[scale=0.6] at (0,-1){\textbullet} (-0.025,-1)node[anchor=north west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
\node[scale=0.6] at (1,-1){\textbullet} (1,-1)node[anchor=north,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};

\node[scale=0.6] at (0,0){\textbullet} (0,0)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,0)$};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \hat \Psi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\node at (-1, 1.35)[opacity=1, scale=0.8]{\scriptsize $\Psi$};
\draw[dashed,opacity=0.2] (-1.2,0) -- (1.2,0) node[scale=0.4, anchor=west, opacity=1]{\scriptsize $u_1$};
\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[scale=0.4,anchor=south, opacity=1]{\scriptsize $u_2$};

@@

%% embedding points
\node[scale=0.6] at (1,1){\textbullet};
\node[scale=0.6] at (1,0){\textbullet};
\node[scale=0.6] at (0,1){\textbullet};
\node[scale=0.6] at (-1,-1){\textbullet};
\node[scale=0.6] at (-1,0){\textbullet};
\node[scale=0.6] at (-1,1){\textbullet};
\node[scale=0.6] at (0,-1){\textbullet};
\node[scale=0.6] at (1,-1){\textbullet};
\node[scale=0.6] at (0,0){\textbullet};
